---
author: "Emma Delaporte"
date: "4/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library('openssl')
library('httpuv')
library('jsonlite')
library('dplyr')
library('quanteda')
library('wordcloud')
library('RColorBrewer')
```

**Create a function to get tweets**
```{r}
#set the parameters
tweets_params <- list(
  `tweet.fields` = 'text,created_at',
  #exclude retweets/replies
  # `exclude` = 'retweets',
  `max_results` = 100
)

#set tokens
Sys.setenv(BEARER_TOKEN = "AAAAAAAAAAAAAAAAAAAAAAD2bwEAAAAAw996QpUhBx0ywniZez6nXzZDhfc%3DmWcjcezQFSXfXVAl5tS3djAQYHkBY4vAL9XRBa2xIO4pRUawIP")
require(httr)
require(jsonlite)
require(dplyr)

#build the function
get_tweets <- function (username) {
  bearer_token <- Sys.getenv("BEARER_TOKEN")
  headers <- c(`Authorization` = sprintf('Bearer %s', bearer_token))
  
  user_response <- httr::GET(
    url = sprintf("https://api.twitter.com/2/users/by/username/%s", username),
    httr::add_headers(.headers = headers)
  )
  obj <- httr::content(user_response, as = "text")
  data <- fromJSON(obj, flatten = TRUE)
  user_id <- data$data$id
  print(sprintf('user ID: %s', user_id))
  
  tweets_url <- sprintf('https://api.twitter.com/2/users/%s/tweets', user_id)
  
  get_tweets_base <- function (pagination_token = NULL) {
    if (!is.null(pagination_token)) {
      tweets_params$pagination_token <- pagination_token
    }
    
    response <- httr::GET(
      url = tweets_url,
      httr::add_headers(.headers = headers),
      query = tweets_params
    )
    obj <- httr::content(response, as = "text")
    data <- fromJSON(obj, flatten = TRUE)
    
    tweets <- as.data.frame(data$data)
    print(sprintf('got %s more tweets', nrow(tweets)))
    
    next_token <- data$meta$next_token
    if (!is.null(next_token)) {
      next_tweets <- get_tweets_base(next_token)
      tweets <- rbind(tweets, next_tweets)
    }
    
    return(tweets)
  }
  
  return(get_tweets_base())
}
```



```{r}

#alphabet workers
all_tweets <- get_tweets('AlphabetWorkers')
#insert union name
all_tweets$union <- "alphabet"

#Big Cartel Union
bc_tweets <- get_tweets('bcworkersunion')
bc_tweets$union <- "bigcartel"

#Code For America Union
cfa_tweets <- get_tweets('CfAWorkers')
cfa_tweets$union <- "cfa"

#Kichstarter Union
kick_tweets <- get_tweets('ksr_united')
kick_tweets$union <- "kickstarter"

#Code CWA tweets
cwa_tweets <- get_tweets('CODE_CWA')
cwa_tweets$union <- "cwa"

#Mapbox workers union
mapbox_tweets <- get_tweets('MapboxUnion')
mapbox_tweets$union <- "mapbox"

#NPR digital media united
dmu_tweets <- get_tweets('WeBuildNPR')
dmu_tweets$union <- "digitalmedianpr"

#activison blizzard
abk_tweets <- get_tweets('ABetterABK')
abk_tweets$union <- "actiblizzard"

#medium
medium_tweets <- get_tweets('mediumworkers')
medium_tweets$union <- "medium"

#blue state
bluestate_tweets <- get_tweets('BlueStateU')
bluestate_tweets$union <- "bluestate"

#nyt tech
nyt_tech_tweets <- get_tweets('NYTGuildTech')
nyt_tech_tweets$union <- "nyt_tech"

#paizo
paizo_tweets <- get_tweets('PaizoWorkers')
paizo_tweets$union <- "paizo"
```

```{r warning=FALSE}
#combine the tech unions ( i need to clean this up lol)

techtweets <- do.call("rbind", list(
  all_tweets,
  bc_tweets,
  cfa_tweets,
  kick_tweets,
  cwa_tweets,
  mapbox_tweets,
  dmu_tweets,
  abk_tweets,
  medium_tweets,
  bluestate_tweets,
  nyt_tech_tweets,
  paizo_tweets
))

#write.csv(techtweets, "techtweets.csv")

#description of the corpus

library(epiDisplay)
tab1(techtweets$union, descending = TRUE, cum.percent = TRUE)

#mean length of tweet
mean(nchar(techtweets$text))

#proportion of retweets to tweets
table(techtweets$RT)


```

**Export the dataset for labeling**
```{r}
#sampling data for testing
#techsample <- techtweets[sample(nrow(techtweets), 300),]
#WriteXLS(techsample, "techsample.xls")

#importing the manually labeled test data 
techsample <- read.csv("techsample.csv")

```

**Data Processing**
```{r}
library(stringr)

#I'm creating a dummy variable for retweets so that 'RT' isn't picked up as a work but is also separable from the data
techtweets$RT <- grepl("^RT @\\w+: ", techtweets$text)

# Now I'm removing RT from the tweets
techtweets$text <- str_remove(techtweets$text, "^RT @\\w+: ")

#Now I'm removing twitter handles
techtweets$text <- str_remove_all(techtweets$text, "@\\w+")

#Remove hyperlinks
techtweets$text <- str_replace_all(techtweets$text, "https://t.co/[a-z,A-Z,0-9]*","")

#remove apostrophes and letters following them
techtweets$text <- gsub("['’]\\w+", "", techtweets$text)

#Remove punctuation expect apostrophe
techtweets$text <- gsub("[[:punct:]]", " ", techtweets$text) 
#techtweets$text <-gsub("(?!')[[:punct:]]", "", techtweets$text, perl=TRUE)


#remove problematic ampersand
techtweets$text <- gsub("amp", " ", techtweets$text) 

#remove blank spaces at beginnings of tweets
techtweets$text <- gsub("^ ", "", techtweets$text)

#remove non-text symbols
techtweets$text <- iconv(techtweets$text, to = "ASCII", sub = " ")


#Manual cleaning after inspecting the data

#change U S into USA for sake of clarity
techtweets$text <- gsub("U S ", " USA ",techtweets$text)

#removing 'w' (which)
techtweets$text <- gsub(" w ", "", techtweets$text)

#removing 't' (leftover from hyperlinks)
techtweets$text <- gsub(" t ", "", techtweets$text)
```

*Further Cleaning and exploratory analysis*
```{r}
library(quanteda.textplots)
library(tm)
library(textstem)

tech_corp <- corpus(techtweets)

tech_toks <- quanteda::tokens(tech_corp, remove_numbers = TRUE, remove_symbols = TRUE)
tech_toks <- tokens_tolower(tech_toks)
tech_toks <- tokens_wordstem(tech_toks, language = "en")
tech_toks <- quanteda::tokens(tech_toks, remove_punct = TRUE)


tech_dfm <- dfm(tech_toks, remove = stopwords("english"))

textplot_wordcloud(tech_dfm, min_count = 15)


#Checking word frequency
```

*Testing out some topic models*
```{r}
library(ldatuning)
library(topicmodels)

#convert quanteda object to topic model object
lda_tech <- convert(tech_dfm, to="topicmodels")

#suggestion for a good number of topics
topnums <- FindTopicsNumber(
  lda_tech,
  topics = seq(from = 2, to = 20, by = 1),
  metrics = c( "CaoJuan2009"),
  method = "Gibbs",
  control = list(seed = 21),
  verbose = TRUE
)

topnums

#from these results i'll try 5 and 11

```




```{r}
topicMod_LDA <- LDA(lda_tech, 6, method="Gibbs", control=list(seed = 500, verbose = 25))

topic_cats <- terms(topicMod_LDA, 30)

topic_cats
```
*I need to figure out whats up with the 't' and 's' (theyre getting seperated by apostrophe)*
*also should i use tf-idf weights?*


*calculate the distribution of categories and assign categories to tweets*
```{r}

#proportion of topics for each tweet
LDA_theta <- posterior(topicMod_LDA)$topics
LDA_theta_df <- as.data.frame(LDA_theta)





#get theta for topics 

cols <- c("theta1", "theta2", "theta3", "theta4", "theta5", "theta6")

  for (idx in 1:nrow(techtweets)) {
    textName <- paste("text", idx, sep = "")
   for (i in 1:ncol(LDA_theta)){
     colname <- paste("theta",i, sep="")
     techtweets[idx,colname] <- LDA_theta[,i][textName]
   }
  }

##maybe ryan can help me 
theta_idx <- c()
techtweets$topic_cat
#assign categories to tweets
for (idx in 1:nrow(techtweets)) {
  theta_idx <- techtweets[,6:11]
  techtweets$topic_cat <- techtweets %>%
    mutate(topic_cat = which.max(theta_idx[idx,]))
}




```

**Alternatively, trying bi-term topic models to see if they improve anything**

```{r}
library('BTM')
library('udpipe')
library(data.table)
library(stopwords)

#annotate terms in the tweets. FIGURE OUT WHAT TRACE MEANSLATER
tagged_tech <- udpipe(techtweets$text, "english", trace = 10)

biterms <- as.data.table(tagged_tech)

biterms <- biterms[, cooccurrence(x = lemma,
                                  relevant = upos %in% c("NOUN", "ADJ", "VERB") & 
                                             nchar(lemma) > 2 & !lemma %in% stopwords("en"),
                                  skipgram = 3),
                   by = list(doc_id)]

```

**Build Biterm topic model with five topics**
```{r}
set.seed(1234)
traindata <- subset(tagged_tech, upos %in% c("NOUN", "ADJ", "VERB") & !lemma %in% stopwords("en") & nchar(lemma) > 2)
traindata <- traindata[, c("doc_id", "lemma")]
bit_model     <- BTM(traindata, biterms = biterms, k = 5, iter = 2000, background = TRUE, trace = 100)

#inspect the model 
#topic frequency
bit_model$theta
#there appears to be one topic that takes up the vast majority of tweets (79%!)

topicterms <- terms(bit_model, top_n = 30)
topicterms

#Visualize the model
library(textplot)
library(ggraph)
library(concaveman)
plot(bit_model)

#assign bi term topics to tweets
bit_tops <- predict(bit_model, traindata)

bi_cols <- c("bit1", "bit2", "bit3", "bit4", "bit5")

  for (idx in 1:nrow(techtweets)) {
    textName <- paste("doc", idx, sep = "")
   for (i in 1:ncol(bit_tops)){
     colname <- paste("bit",i, sep="")
     techtweets[idx,colname] <- bit_tops[,i][textName]
   }
  }
```


*Compare the distribution of themes in the testing data, biterm model and LDA model*
```{r}
#The categories that I have created manually, using grounded-theory thematic analysis from the sample data, are the following"
  #Solidarity
  #Diversity and sociopolitical issues
  #employer misconduct and worker protection
  #collective bargaining/ pay and benefits 
  #other (everything that doesn't fit) 

#view distribution of samples
techsample <- read.csv("techsample_label.csv")

library(dplyr)
catfreq <- techsample %>%
  group_by(category) %>%
  summarise(counts = n())

library(epiDisplay)
tab1(techsample$category, cum.percent = TRUE)

```
*The results of my manual labeling of a sample of the data show that solidarity is by far the most prevalent topic, at 44% of the data, followed by the "employer misconduct and worker protection" and "other" category at 15%*

